\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-03-26 doc/sw-system.tex
Added notes to intro and conclusions. Fixes #104

In this paper, we describe the \sw web application, an online system that was
conceived to address the visual inspection problem in gravitational lens
detection for future large surveys via crowd-sourcing, and implemented as a
Zooniverse project. In a companion paper (More et al, in preparation, herafter
\PaperTwo) we will present the new gravitational lenses discovered in our first,
experimental, lens search, and begin to investigate the differences between lens
detections made in \sw and those made with automated techniques. Here though, we
simply try to answer the following questions:

@@

Sum up, end.

>>>>

In this paper, we describe the \sw project, an web-based system  conceived to
address the visual inspection problem in gravitational lens detection for future
large surveys via crowd-sourcing. Implemented as a Zooniverse project, it is
designed to provide a {\it gravitational lens discovery service} to survey teams
looking for lenses in wide field imaging data. In a companion paper (More et al,
in preparation, herafter \PaperTwo) we will present the new gravitational lenses
discovered in our first, experimental, lens search, and begin to investigate the
differences between lens detections made in \sw and those made with automated
techniques. Here though, we simply try to answer the following questions:

@@

Sum up, end. \SW provides a lens candidate detection service, crowd-sourcing the
time-consuming work of visually inspecting astronomical images for
gravitationally-lensed features. We invite survey teams searching for lenses in
their wide-field imaging data to contact us if they would like our help.
